Outstanding Title

### 2017-04-17 writing/EpiDraft.Rmd
Scrape one value from CDC webpage like a boss

>>>>

```{r}
#scrape just the New York City value for week 14 of 2017 from cdc website:
library(rvest)
url <- read_html("https://wonder.cdc.gov/mmwr/mmwr_2017.asp?mmwr_year=2017&mmwr_week=14&mmwr_table=2J&request=Submit&mmwr_location=")
nyc <- html_nodes(url, 'tr:nth-child(15) td:nth-child(2)')
as.numeric(html_text(nyc))
```
